---
title: "lab1"
author: "Qinhao Xu"
date: "7/2/2017"
output: html_document
---
1.1 Proof of Installation

```{r}
system("who",intern = TRUE)
```

1.2 Installing Packages and Loading them using library
```{r}
find.package("tidyverse")
find.package("haven")
find.package("foreign")
```
2. Application of Badic R Rules
A.
```{r}
12^8/3^7
```
B.
```{r}
64838 - 7314
```
C.
```{r}
17^(6/5)
```
D.
```{r}
13%/%4
```
E.
```{r}
8675+3090-1999+101405+5551-21979+24334
```
2.2 Vectors
2.2.1 Numeric Vectors
A.
```{r}
junk <- c(10,23,45,52,63,25,63,64,2,5)
junk
```
B.
```{r}
junk1 <- seq(1,1000,2)
junk1
```
C.
```{r}
m <- 7
junk2 <- c((seq(-m, -1, 1))^3 , 0, (seq(1, m , 1))^3)
junk2
```
D.
```{r}
(junk/3)^2
```
E.
library(magrittr)
plyr::mapvalues(junk, from = c(junk[4], junk[9] ), to = c( (junk[4])^2, (junk[9])^2 ))
```{r}
junk[c(4,9)] <- junk[c(4,9)]^2
junk
```
2.2.2  Character (String) and Logical Vectors

A.
```{r}
char <- c("alpha","beta","gamma","delta", "epsilon", "zeta","eta", "theta")
char
```
B.
```{r}
char[7:8]
```
C.

b consisits of logical constants TRUE and FALSE, which they represent 0 and 1.

d is a matrix that consists of numbers and characters. Since character has higher order than numerics, thus the entire matrix is a character matrix

2.3 Matrices 

A.
1.
```{r}
mt<- c(5:1, seq(10, 2, -2), seq(15,3,-3), seq(20,4,-4), seq(25,5,-5) )
mt1 <- matrix(mt, ncol = 5, byrow = TRUE)
mt1
```
2.
```{r}
a<-5:1
b<-seq(10, 2, -2)
c<- seq(15,3,-3)
d<- seq(20,4,-4)
e <- seq(25,5,-5)
mt2<- cbind(a,b,c,d,e)
mt2

```
matrix(c(a,b,c,d,e), ncol =5, byrow = TRUE)
3.
```{r}
mt3 <- rbind(a,b,c,d,e)
mt3
```
B.
```{r}
mt1[4,]
```
C.
```{r}
mt1[,c(2,4)]
```
2.4 Data Frames
A.
```{r}
data("USArrests")
```
B.
```{r}
class(USArrests)
typeof(USArrests)
```
C.
```{r}
str(USArrests[,,drop= FALSE])
```
3.1 Find The Function

```{r}
exp <- 0:9
exp(exp)
round(exp(exp), digits =2)
```

3.2 Find the Operator 
```{r}
J <- 25 %% 773
K <- 5^3 %% 773
p1 <- K^2 %% 773
p2 <- J^3 %% 773
p1
p2
```


