---
title: "lab4"
author: "Qinhao Xu"
date: "7/20/2017"
output: html_document
---
1. Variable Creation and Transformation


A.
```{r}
load(url("http://www.stat.ucla.edu/~vlew/datasets/water2013.RData"))
Water$ZIP <- substr(Water$`Location 1`, 1,5)
head(Water, n=2)
```
B.
```{r}
Water$PCTCHANGE <- Water$`FY 12/13`/ Water$`FY 11/12`
head(Water, n=2)
```

C.
```{r}
a <- data.frame(Water,Water$ZIP) 
b <- data.frame(zipraceincome,zipraceincome$ZIP) 
Common <- merge(a,b, by="ZIP") 
head(Common, n=2)
```
D.

(1)
```{r}
nonsaver<-Common[which(Common$PCTCHANGE >= 0.80), ]
table(nonsaver$ZIP)
median(nonsaver$MEDINC)
```


(2)
```{r}
supersaver<-Common[which(Common$PCTCHANGE <= 0.40), ]
table(supersaver$ZIP)
median(supersaver$MEDINC)
```


(3)
```{r}
median(Common$MEDINC)
```

(4)

There are more non saver zip code than super saver zip code, which means there are more non-saver than super-savers.

2. String , Dates and Time 
A.
```{r}
library(chron)
library(dplyr)
library(ggplot2)
library(knitr)
FDCALLS2016<-read.csv("/Users/Qinhaoxu/Desktop/FDCALLS2016.csv",stringsAsFactors = FALSE)
FDCALLS2016$Time <- strptime(FDCALLS2016$Received.DtTm, format = "%m/%d/%Y %I:%M:%S %p",tz ="")
FDCALLS2016$MONTH <- months(FDCALLS2016$Time)
FDCALLS2016$Day <- weekdays(FDCALLS2016$Time)
FDCALLS2016$Hour <- hours(FDCALLS2016$Time)
S <-FDCALLS2016[which(FDCALLS2016$Call.Type == "Structure Fire"),]
sort(table(S$MONTH))
```
July has the highest structure fire calls

B.
```{r}
library(ggplot2)
S$Days <- factor(S$Day, levels = c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday"))
ggplot(S) + geom_hex(aes(x=Days, y=Hour),color="black") + scale_fill_gradientn(colours = rainbow(7))+theme(axis.text.x = element_text (size =  6) )
```




Sunday 15pm has the highest structure fire calls

C.
```{r}
neig<- FDCALLS2016[which(FDCALLS2016$Neighborhooods...Analysis.Boundaries!="None"),]
k<-table(neig$Neighborhooods...Analysis.Boundaries)
s_neig<-as.data.frame(k)

s_neig1<- neig[which(neig$Call.Type == "Medical Incident"),]
k1<-table(s_neig1$Neighborhooods...Analysis.Boundaries)
s_neig2<-as.data.frame(k1)
s_neig$prop1 <- s_neig2$Freq/s_neig$Freq
s_neig<-s_neig[order(s_neig$prop1),]
#lowest
head(s_neig,n=1)
#highest
tail(s_neig,n=1)
```

3. String and Factorsz
A.
```{r}
library(knitr)
library(XML)
library(dplyr)
library(readr)
wsj <- readHTMLTable("http://online.wsj.com/public/resources/documents/info-Salaries_for_Colleges_by_Region-sort.html")
example1<-wsj[[7]] %>% as.data.frame()
str(example1)
example1[1:10,1:5] %>% kable
examplefixed<-lapply(example1,gsub, pattern=c('Â'),replacement=c(''))
examplefixed<-lapply(examplefixed,gsub, pattern=c(','),replacement=c(''))
ipeds <- read.csv("/Users/Qinhaoxu/Desktop/ipeds.csv")
college <- merge(examplefixed,ipeds, by="School.Name") 
dim(college)
```

B.
```{r}
college$Institutional.control.or.affiliation <- factor(college$Institutional.control.or.affiliation,levels = c(1,3,4), labels = c("Public", "Private, Non-
Religous","Private, Religious"))
table(college$Institutional.control.or.affiliation)
```

C.
Public Best and Worse colleges in state and out state
```{r}
college$Starting.Median.Salary<-gsub("\\$","",college$Starting.Median.Salary)
p_c<-college[which(college$Institutional.control.or.affiliation=="Public"),]
p_r<-college[which(college$Institutional.control.or.affiliation=="Private, Religious"),]
p_n_r<-college[which(college$Institutional.control.or.affiliation=="Private, Non-\nReligous"),]

p_c$Starting.Median.Salary<-as.numeric(p_c$Starting.Median.Salary)
p_c$Total.price.for.in.state.students.living.on.campus.2013.14<- as.numeric(p_c$Total.price.for.in.state.students.living.on.campus.2013.14)
p_c$Total.price.for.out.of.state.students.living.on.campus.2013.14 <- as.numeric(p_c$Total.price.for.out.of.state.students.living.on.campus.2013.14)
p_c$instate<-(p_c$Total.price.for.in.state.students.living.on.campus.2013.14 * 4)/p_c$Starting.Median.Salary
p_c$outstate<-(p_c$Total.price.for.out.of.state.students.living.on.campus.2013.14 * 4)/p_c$Starting.Median.Salary

#public best and worse colleges in state
p_college_in<- p_c[,c(1,20,21)]
p_college_in<- p_college_in[order(p_college_in$instate),]
head(p_college_in,n=3)
tail(p_college_in,n=3)
#public best and worse colleges out state
p_college_out<- p_c[,c(1,20,22)]
p_college_out<- p_college_out[order(p_college_out$outstate),]
head(p_college_out,n=3)
tail(p_college_out,n=3)
```

Best and Worse private religous colleges in state and out state
```{r}
p_r$Starting.Median.Salary<-as.numeric(p_r$Starting.Median.Salary)
p_r$Total.price.for.in.state.students.living.on.campus.2013.14<-as.numeric(p_r$Total.price.for.in.state.students.living.on.campus.2013.14)
p_r$Total.price.for.out.of.state.students.living.on.campus.2013.14<-as.numeric(p_r$Total.price.for.out.of.state.students.living.on.campus.2013.14)
p_r$instate<-(p_r$Total.price.for.in.state.students.living.on.campus.2013.14 * 4)/p_r$Starting.Median.Salary
p_r$outstate<-(p_r$Total.price.for.out.of.state.students.living.on.campus.2013.14 * 4)/p_r$Starting.Median.Salary

#private religious colleges  best and worse in state 
p_r_in<- p_r[,c(1,20,21)]
p_r_in<- p_r_in[order(p_r_in$instate),]
head(p_r_in,n=3)
tail(p_r_in,n=3)

#private religious colleges  best and worse out state 
p_r_out<- p_r[,c(1,20,22)]
p_r_out<- p_r_out[order(p_r_out$outstate),]
head(p_r_out,n=3)
tail(p_r_out,n=3)
```


Best and Worse private non-religous colleges in state and out state
```{r}
p_n_r$Starting.Median.Salary<-as.numeric(p_n_r$Starting.Median.Salary)
p_n_r$Total.price.for.in.state.students.living.on.campus.2013.14<-as.numeric(p_n_r$Total.price.for.in.state.students.living.on.campus.2013.14)
p_n_r$Total.price.for.out.of.state.students.living.on.campus.2013.14<-as.numeric(p_n_r$Total.price.for.out.of.state.students.living.on.campus.2013.14)
p_n_r$instate<-(p_n_r$Total.price.for.in.state.students.living.on.campus.2013.14 * 4)/p_n_r$Starting.Median.Salary
p_n_r$outstate<-(p_n_r$Total.price.for.out.of.state.students.living.on.campus.2013.14 * 4)/p_n_r$Starting.Median.Salary

#private non religious colleges  best and worse in state 
non_r<- p_n_r[,c(1,20,21)]
non_r<- non_r[order(non_r$instate),]
head(non_r,n=3)
tail(non_r,n=3)

#private non religious colleges  best and worse out state 
non_o<- p_n_r[,c(1,20,22)]
non_o<-non_o[order(non_o$outstate),]
head(non_o,n=3)
tail(non_o,n=3)

```











